### 2022-01-17 input/proposal.tex
meow
Add distance-vector in related work and remove stuff about Xascast in III

To provide lazy and dynamic logical partitioning in dynamic networks
using scoped broadcast, all live \processes must collaborate to
disseminate messages that notify new or removed sources to all and
only interested \processes. This section reviews step-by-step the
properties that allow \processes to converge to the desired state
together. It first defines scoped broadcast, then uses it to guarantee
consistent partitioning when a \process can only become a new source
in the system. It highlights the issue when a \process can also remove
its status of source. It shows that using local knowledge and scoped
broadcast, \processes can still reach dynamic consistent partitioning
when they are able to detect possible blocking conditions in the
dissemination of required notifications. \TODO{Finally, it further constrain
the system by allowing only subsets of \processes to reach lazy
consistent partitioning. This improvement only requires \processes to
know which of their neighbors belong to their own network.}

@@

\NAME follows the principles of scoped broadcast to efficiently and
consistently propagate notifications to \processes that need them
despite concurrent operations. \TODO{Next section aims at providing
empirical evidence of the scalability and properties of \NAME.}

>>>>

To provide lazy and dynamic logical partitioning in dynamic networks
using scoped broadcast, all live \processes must collaborate to
disseminate messages that notify new or removed sources to all and
only interested \processes. This section reviews step-by-step the
properties that allow \processes to converge to the desired state
together. It first defines scoped broadcast, then uses it to guarantee
consistent partitioning when a \process can only become a new source
in the system. It highlights the issue when a \process can also remove
its status of source. It shows that using local knowledge and scoped
broadcast, \processes can still reach dynamic consistent partitioning
when they are able to detect possible blocking conditions in the
dissemination of required notifications.

@@

\NAME follows the principles of scoped broadcast to efficiently and
consistently propagate notifications to \processes that need them
despite concurrent operations. Next Section aims at providing the
empirical evidence of scalability and properties of the proposed
approach.
